iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-29 manuscript/main.tex

\subsection*{Additional functionalities}
Row statistics tables can be augmented with dynamic annotation based on the selected row, linking to online resources such as Ensembl or Entrez. % do we need to cite them? at least ENSEMBL has updated citable papers
For large datasets, points can be downsampled in a density-dependent manner to accelerate rendering of the plots, improving the responsiveness of the interface without compromising the fidelity of the visualization.
Users can also include a bespoke step-by-step ``tour'' of their data set via the rintrojs package \cite{ganz2016rintrojs}, guiding the audience through an examination of the salient features in the data.

@@

\section*{Conclusion}
iSEE provides a general interactive interface for visual exploration of a diverse range of `-omics datasets.
We provide a number of demonstrations at \url{https://github.com/LTLA/iSEE2018}, using iSEE to explore the TCGA RNA-seq collection \citep{piccolo2015TCGA}, the 4,000 PBMC single-cell RNA sequencing dataset from 10X Genomics \citep{zheng2017massively} and a published mass cytometry dataset consisting of over 170,000 cells \citep{bodenmiller2012cytof}.
% TODO: repurpose the conclusion if we showcase the examples in earlier sections
% TODO: sell the idea that for every dataset it is possible to explore and showcase feats of interest. Something like...
We expect the functionalities and flexibility of the iSEE package to be essential for exploring and showcasing relevant features of any data set that can be represented in the form of a SummarizedExperiment object.
In particular, we expect public instances of iSEE to ideally accompany publications, as they enable authors to reproduce published figures and showcase salient aspects of their work using guided tours, while fostering hypothesis generation through transparent, interactive, reproducible, and efficient data analysis by the broader reader audience.

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.

>>>>

\subsection*{Additional functionalities}
Row statistics tables can be augmented with dynamic annotation based on the selected row, linking to online resources such as Ensembl or Entrez. % do we need to cite them? at least ENSEMBL has updated citable papers
For large data sets, points can be downsampled in a density-dependent manner to accelerate rendering of the plots, improving the responsiveness of the interface without compromising the fidelity of the visualization.
Users can also include a bespoke step-by-step ``tour'' of their data set via the rintrojs package \cite{ganz2016rintrojs}, guiding the audience through an examination of the salient features in the data.

@@

\section*{Conclusion}
iSEE provides a general interactive interface for visual exploration of a diverse range of `-omics data sets.
We provide a number of demonstrations at \url{https://github.com/LTLA/iSEE2018}, using iSEE to explore the TCGA RNA-seq collection \citep{piccolo2015TCGA}, the 4,000 PBMC single-cell RNA sequencing data set from 10X Genomics \citep{zheng2017massively} and a published mass cytometry data set consisting of over 170,000 cells \citep{bodenmiller2012cytof}.
% TODO: repurpose the conclusion if we showcase the examples in earlier sections
% TODO: sell the idea that for every data set it is possible to explore and showcase feats of interest. Something like...
We expect the functionalities and flexibility of the iSEE package to be essential for exploring and showcasing relevant features of any data set that can be represented in the form of a SummarizedExperiment object.
In particular, we expect public instances of iSEE to ideally accompany publications, as they enable authors to reproduce published figures and showcase salient aspects of their work using guided tours, while fostering hypothesis generation through transparent, interactive, reproducible, and efficient data analysis by the broader reader audience.

\subsection*{Author contributions}
All authors contributed conceptually and technically to the development and maintenance of large sections of the package code.
A.T.L.L. and F.M. developed the application and data infrastructure.
K.R.A and C.S. developed the plotting framework.
F.M. developed the code tracking and user interface.
K.R.A designed and developed the ExperimentColorMap class.
All authors contributed to testing the application on all data sets.
All authors wrote and approved the final manuscript.
